Ideological Positioning and Racial Media Framing in the Opioid Epidemic Influences Policy Outlooks

### 2024-02-20 paper/paper.qmd
Final commits to paper.pdf and paper.qmd, Feb 19 @ 7:31pm.

$H_2$ stated there would be a significant interaction effect between political ideology and unsympathetic media framing, expecting that liberals would be less swayed by unsympathetic narratives towards punitive measures. However, `conservative:unsympathetic_black` is the only unsympathetic media frame to show a positive effect and whose confidence intervals do not cross the zero point, disproving this hypotheses. `liberal:unsympathetic_white, liberal:unsympathetic_black, and 'conservative:unsympathetic_white' all show a positive effect, however, their confidence intervals all cross the zero point. at this point it is acceptable to reject $H_2$, as the data does not show a clear differential impact of unsympathetic framing between the ideologies.

The data reveals that political ideology and media framing can influence attitudes towards treatment-focused policies. This is especially true when liberals are exposed to media that frames a white opioid user in a sympathetic lens, providing partial support for the first hypothesis $H_1$. The most interesting find was conservatives positive relationship regarding support for treatment related policy when faced with media framing black opioid users in an unsympathetic lens. In summary, this analysis reveals that political ideology does somewhat interact with media framing to influence support for treatment related policies, the interactions require further research and analysis to draw stronger conclusions. It is important to note that the lack of statistical significance for most comparisons, due to confidence intervals crossing the zero point, indicates a need for caution in over-interpreting these results.

>>>>

$H_2$ stated there would be a significant interaction effect between political ideology and unsympathetic media framing, expecting that liberals would be less swayed by unsympathetic narratives towards punitive measures. However, `conservative:unsympathetic_black` is the only unsympathetic media frame to show a positive effect and whose confidence intervals do not cross the zero point, disproving this hypotheses. `liberal:unsympathetic_white, liberal:unsympathetic_black, and 'conservative:unsympathetic_white' all show a positive effect, however, their confidence intervals all cross the zero point. At this point it is acceptable to reject $H_2$, as the data does not show a clear differential impact of unsympathetic framing between the ideologies.

The data reveals that political ideology and media framing can influence attitudes towards treatment-focused policies. This is especially true when liberals are exposed to media that frames a white opioid user in a sympathetic lens, providing partial support for the first hypothesis $H_1$. The most interesting find was conservatives positive relationship regarding support for treatment related policy when faced with media framing black opioid users in an unsympathetic lens. In summary, this analysis reveals that political ideology does somewhat interact with media framing to influence support for treatment related policies. However, theses interactions require further research and analysis to draw stronger conclusions. It is important to note that the lack of statistical significance for most comparisons, due to confidence intervals crossing the zero point, indicates a need for caution in over-interpreting these results.
